Exposing Disputed Statements on the Web

### 2009-03-21 papers/uist_thinklink/thinklink.tex
More paper, screenshot, and bug fix work

\todo{Talk about searches}
\todo{Cite work on collaborative filtering}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
	\caption{Use topic suggestion to quickly file evidence snippets}
	\label{sniptopic}
	\end{center}
\end{figure}

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=16cm]{../screenshots/newsnip_all.png}
	\caption{Process for creating a new snippet}
	\label{createprocess}
	\end{center}
\end{figure*}

>>>>

\todo{Talk about searches}
\todo{Cite work on collaborative filtering}
\todo{Mention the sidebar?}

@@

If an activist user has installed the Think Link browser extension then they can mark up snippets that they believe make disputed claims, causing them to be highlighted when viewed by other readers. A user can mark a snippet as disputed by selecting the text, and clicking ``This is disputed'' in the context menu.

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_snipmark.png}
	\caption{Use the context menu to mark a new snippet}
	\label{createprocess}
	\end{center}
\end{figure*}

In order for the snippet to be useful for other readers, one needs to state what claim it is making. Since a user will often want to collect many snippets that make the same point, Think Link allows a user to associate snippets with claims in bulk, rather than having to specify a snippet every time they create a snippet.

When a user creates a snippet, it is initially highlighted in blue, to show that it has not yet been associated with a claim. Such unattached snippets are only visible to the user who created them. A user can chose to associate a snippet with a claim immediately by clicking on it and selecting from a list of suggested snippets. Alternatively, they can use the claim browser to assign snippets to claims in bulk (Figure~\ref{sniptopic}).

% Put all user study stuff at the end

In order for the snippet to be useful for other readers, one needs to state what claim it is making. Early versions of Think Link required a user to state the disputed claim that a snippet was making at the point at which they marked it; however our studies revealed that this made the process of marking snippets too arduous and deterred users from marking snippets. Recent versions of TWe thus instead created an interface that allows a user to mark up snippets without saying what claim they are making and then assign snippets to claims ``in bulk'' (Figure~\ref{sniptopic}.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
	\caption{The claim browser shows a list of unfiled snippets}
	\label{sniptopic}
	\end{center}
\end{figure}

When a user creates a snippet, it is intially highlighted in blue, to show that it has not yet been associated with a snippet and will not be visible to other users. If the user clicks on the highlighted snippet then

If an activist user is looking for snippets that make a particular claim that they disagree with then they may collect many snippets that are making the same claim. Rather than requiring

It is important to make this process as simple and easy as possible.

 Rather than requiring a user to specify the claim a snippet is making when the snippet is created, Think Link allows users to mark snippets without saying what it is they claim and then associate snippets with claims ``in bulk''.

It is important to make the process of creating snippassociating snippets with claims as easy as possible. If

 In early versions of Think Link we required a user to state the claim a snippet was making when they marked it; however our user studies revealed that this made the process of creating snippets take too long and put users off creating them.

In early versions of Think Link we required a user to state the claim a snippet was making at the point at which they created the snippet; however our user studies revealed that

Think Link allows an activist user to highlight snippets that they believe make contentious claims so that other readers will be exposed to the evidence on the other side. If a user finds a snippet of text that they believe is making a disputed claim then they can select the text, and select ``This is disputed'' from the

@@
